### 2020-07-12 paper/sex_selection_spacing-ver4.tex
Minor edit

I focus on the three birth intervals starting from the first birth and ending with the 
fourth birth.
I exclude the interval from marriage to the first birth because many are imputed and,
with falling fertility, few women had five or more births, especially among the 
better-educated.

>>>>

I focus on the three birth intervals starting from the first birth and ending with the 
fourth birth.
I exclude the interval from marriage to the first birth because many are imputed and
higher order intervals because, with falling fertility, few women had five or more 
births, especially among the better-educated.
